---
title: "Class10"
author: "Natalie McGrath"
date: "2026-09-28"
output: html_document:
    toc:TRUE 
    toc_float: TRUE 
    number_sections: TRUE 
    code_download: TRUE 
    code_folding: show 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Robotstxt

The code chunk below will show the output from the [robotstxt package]() for the ISA bulletin available at: <https://bulletin.miamioh.edu/courses-instruction/isa/index.html  
```{robotstxt}
##Can you scrape this webpage or not? 
robotstxt::paths_allowed(paths = "/courses-instruction/isa/", domain = "bulletin.miamioh.edu", bot = "*")
```

```{r wiki}

robotstxt::paths_allowed(paths = "/wiki/Miami_RedHawks_football", domain = "en.wikipedia.org", bot = "*")

#This one does allow scraping 

```
```{r indeed }
robotstxt::paths_allowed(paths = "/jobs and /viewjob", domain = "www.indeed.com", bot = "*")
#Also allows scraping we already know that linkedin does not based on notes 
```
In the example above the robots.txt response is inconsistent with what the webpage states. As a general bot, we are not allowed to scrape anything from linkedin. If you removed the slash after the .com the warning disappeared and we got a consistant result of false

```{r}
url = "https://en.wikipedia.org/wiki/Miami_RedHawks_football"
robotstxt::paths_allowed(paths = "/wiki/Miami_RedHawks_football",
                         domain = "en.wikipedia.org", bot = "*")
page = rvest::read_html(url)
items = page |> rvest::html_elements("table.wikitable")
items |> rvest::html_attr("href")
```

## 'rvest' demo: ISA Course Bulletin 

##[a] highligthed the course 
##[b] right clicked and selected inspect 
##[c] found the part that was flushed containing the title 
##[d] right clicked and copied the selector 
##[e] I saw that the output from the code below just got me the 24th course so I dropped the 

```{r}
isa_page_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")
#Extract titles if all titles look the same on the page it means they have the same tag/class which would allow you to extract them in one step
isa_page_in_r |>
  rvest::html_elements("#sc_sccoursedescs > div > p.courseblocktitle >strong"
  ) |> 
  rvest::html_text2() -> isa_titles

isa_page_in_r |> 
  rvest::html_element(".courseeblockdesc") |>
  rvest::html_text2() -> isa_descs

isa_df = data.frame(
  title = isa_titles, description = isa_descs
)

  
```


