---
title: "Class 11"
author: "Natalie McGrath"
date: "2026-09-30"
output: 
  html_document:
    toc:TRUE 
    toc_float: TRUE 
    number_sections: TRUE 
    code_download: TRUE 
    code_folding: show 
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives for Today 
- Scrape multiple webpages using 'for' loops; 
- scrape multiple webpages using the 'purr::map_()' type functions, which would also make your write your own custom fucntions in R 

## Extending the Course Bulletin Scrape for multiple departments 

For the sake of this example, let us scrape the following pages: 
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/)
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/) 

From the logic shown in class, you can essentially do that for all FSB deparemtnets 
Note that if you are doing it for just a few departments, you can just repeat your code a few times; however, this is a bad practice so we will not do this in class. Software engineers tend to refer this as: **DRY** (don't repeat yourself)

```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt')
courses_df= data.frame() #initialize the container 
for(dept_name in dept_abbr) {
  
  cat(rep("-", 25))
  cat("\n")
  
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", 
    dept_name,
    "/"
  )
  
  webpage = rvest::read_html(dept_url)
  
  webpage |> 
    rvest::html_elements("strong") |> 
    rvest::html_text2() -> titles 
  
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs 
  
  df = data.frame(title = titles, desc = descs)
  df$title[1] |> print() #showing only the first course title 
  
  courses_df = rbind(courses_df, df)
  
  cat(rep("-", 25))
  cat("\n")
}


```

## Rexamining the prior example with the 'purrr' package

My preferred approach with the purrr functions is to first create my own function and then use it within the package 


```{r}
scrape_mu_bulletin = function(dept_url){

  webpage = rvest::read_html(dept_url)
  
  webpage |> 
    rvest::html_elements("strong") |> 
    rvest::html_text2() -> titles 
  
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs 
  
  df = data.frame(title = titles, desc = descs)
  
  return(df)
}

test = scrape_mu_bulletin(
  "https://bulletin.miamioh.edu/courses-instruction/bus/"
)

dept_abbr = c('acc', 'bus', 'isa', 'mkt')

my_urls = paste0(
  "https://bulletin.miamioh.edu/courses-instruction/", 
  dept_abbr, 
  "/"
)

courses_df_from_purrr = purrr::map_df(
  .x = my_urls, 
  .f = scrape_mu_bulletin
)

head(courses_df_from_purrr)  


#The map function can take or or more inputs(depending on the function you are using)
# in this example, we only have 1 input for our function 
# so we used map_() instead of map2_() [2 is if you have two inputs] p_map() [for more three or more inputs]
# .x = the vector you are iterating over 

```



