
---
title: "Midwest Airbnb Analysis"
author: "Natalie McGrath"
date: "2026-09-27"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
con = DBI::dbConnect(
  RSQLite::SQLite(),
  "C:/Users/natmc/OneDrive/Desktop/portfolio/apps/midwest_airbnb_chat/data/midwest_airbnb_extended.db"
)

listings = DBI::dbReadTable(con, "listings") |>
  tibble::as_tibble()

availability = DBI::dbReadTable(con, "availability_monthly") |>
  tibble::as_tibble()

reviews = DBI::dbReadTable(con, "reviews_monthly") |>
  tibble::as_tibble()

DBI::dbDisconnect(con)

```

## Question 1 
```{r}
# Count listings owned by each host
host_counts = listings |>
  dplyr::count(host_id, name = "listing_count")

listings_with_counts = listings |>
  dplyr::left_join(host_counts, by = "host_id")

# A1: Number of hosts with 10 or more listings
A1 = host_counts |>
  dplyr::filter(listing_count >= 10) |>
  dplyr::summarize(number_of_hosts = dplyr::n())

# A2: Percentage of Chicago listings owned by those hosts
A2 = listings_with_counts |>
  dplyr::filter(city == "Chicago") |>
  dplyr::summarize(
    percentage = 100 * mean(listing_count >= 10)
  )

A1
A2
```
Answer 1: How many hosts have 10 or more listings across all three cities? 198 Hosts 

Answer 2: What percentage of Chicago's listings belong to these hosts? 31.89%

## Question 2 
```{r}
# Filter listings that meet the requirements
family_listings = listings |>
  dplyr::filter(
    room_type == "Entire home/apt",
    accommodates >= 4,
    number_of_reviews >= 10,
    review_scores_rating >= 4.8
  ) |>
  dplyr::mutate(
    price_per_person = price / accommodates
  )

# Calculate median price per person by neighborhood
neighbourhood_values = family_listings |>
  dplyr::group_by(city, neighbourhood) |>
  dplyr::summarize(
    median_price_per_person = median(price_per_person, na.rm = TRUE),
    listing_count = dplyr::n(),
    .groups = "drop"
  ) |>
  dplyr::filter(listing_count >= 20)

# A3: Find the cheapest qualifying Columbus neighbourhood
A3 = neighbourhood_values |>
  dplyr::filter(city == "Columbus") |>
  dplyr::arrange(median_price_per_person)

A3
```

Answer 3: What is the the name of the Columbus neighbourhood with the lowest median price per person? North Linden, with a median price per person $32.55

## Question 3 
```{r}
# Calculate median values by city and room type
revenue_summary = listings |>
  dplyr::group_by(city, room_type) |>
  dplyr::summarize(
    dplyr::across(
      c(price, reviews_per_month, estimated_revenue_l365d),
      ~ median(.x, na.rm = TRUE)
    ),
    .groups = "drop"
  )

# A4: Median revenue for Twin Cities entire homes
A4 = revenue_summary |>
  dplyr::filter(
    city == "Twin Cities",
    room_type == "Entire home/apt"
  )

A4
```

Answer 4: What is the median estimated revenue of Twin Cities in the entire homes category? 19619 

## Question 4 
```{r}
# Rank listings by estimated revenue within each city
ranked_listings = listings |>
  dplyr::group_by(city) |>
  dplyr::arrange(
    dplyr::desc(estimated_revenue_l365d),
    .by_group = TRUE
  ) |>
  dplyr::mutate(
    top_10_percent = dplyr::row_number() <=
      ceiling(0.10 * dplyr::n())
  ) |>
  dplyr::ungroup()

# Calculate the revenue percentage for each city
revenue_concentration = ranked_listings |>
  dplyr::group_by(city) |>
  dplyr::summarize(
    top_revenue = sum(
      estimated_revenue_l365d[top_10_percent],
      na.rm = TRUE
    ),
    total_revenue = sum(
      estimated_revenue_l365d,
      na.rm = TRUE
    ),
    percentage = 100 * top_revenue / total_revenue,
    .groups = "drop"
  )

# A5: Columbus
A5 = revenue_concentration |>
  dplyr::filter(city == "Columbus")

A5
```

Answer 5: What is the percent of Columbus's total estimated revenue earned by its top 10 %? 36.08% 

## Question 5 
```{r}
# Filter October 2026 availability
october_availability = availability |>
  dplyr::filter(month == "2026-10")

october_homes = listings |>
  dplyr::filter(room_type == "Entire home/apt") |>
  dplyr::inner_join(
    october_availability,
    by = "id"
  ) |>
  dplyr::mutate(
    mostly_taken = nights_available < 0.5 * nights_in_month
  )

# Calculate percentage of mostly-taken homes by city
city_availability = october_homes |>
  dplyr::group_by(city) |>
  dplyr::summarize(
    percentage = 100 * mean(mostly_taken, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::arrange(percentage)

# A6 and A7
city_availability
```


Answer 6: What is the city with the lowest share of mostly taken entire homes? Columbus 


Answer 7: What is that share percentage? 19.02%

## Question 6 
```{r}
# Join reviews to listings and filter the date range
monthly_reviews = reviews |>
  dplyr::inner_join(
    listings |> dplyr::select(id, city),
    by = "id"
  ) |>
  dplyr::filter(
    month >= "2025-07",
    month <= "2026-06"
  )

# Total reviews per city and month
city_monthly_reviews = monthly_reviews |>
  dplyr::group_by(city, month) |>
  dplyr::summarize(
    total_reviews = sum(reviews, na.rm = TRUE),
    .groups = "drop"
  )

# Find the busiest and quietest Twin Cities months
twin_cities_reviews = city_monthly_reviews |>
  dplyr::filter(city == "Twin Cities") |>
  dplyr::arrange(dplyr::desc(total_reviews))

# A8: Busiest month
A8 = twin_cities_reviews |>
  dplyr::slice(1)

# A9: Busiest-to-quietest ratio
A9 = twin_cities_reviews |>
  dplyr::summarize(
    ratio = max(total_reviews) / min(total_reviews)
  )

A8
A9
```

Answer 8: What is the Twin Citiies busiest month? August 


Answer 9: What is the ratio of the busiest month to the quietest month? 2.37 to 1 ratio 

## Question 7 
```{r}
# Filter entire homes with known Superhost status
superhost_listings = listings |>
  dplyr::filter(
    room_type == "Entire home/apt",
    host_is_superhost %in% c("t", "f")
  )

# Calculate median price and rating for each group
superhost_summary = superhost_listings |>
  dplyr::group_by(city, host_is_superhost) |>
  dplyr::summarize(
    median_price = median(price, na.rm = TRUE),
    median_rating = median(review_scores_rating, na.rm = TRUE),
    .groups = "drop"
  )

# Calculate the Superhost price premium for each city
B1 = superhost_summary |>
  dplyr::select(city, host_is_superhost, median_price) |>
  tidyr::pivot_wider(
    names_from = host_is_superhost,
    values_from = median_price
  ) |>
  dplyr::mutate(
    premium = t - f
  ) |>
  dplyr::arrange(city)

superhost_summary
B1
```

Answer B1: 

Chicago: 43.75
Columbus: 40.50
Twin Cities: -1.38

## Question 8 
```{r}
# Find listings with no availability records
missing_availability = listings |>
  dplyr::anti_join(availability, by = "id")

# A10: Count missing listings
A10 = missing_availability |>
  dplyr::summarize(
    missing_listings = dplyr::n()
  )

# Find which city loses the most listings
missing_by_city = missing_availability |>
  dplyr::count(city, name = "missing_listings") |>
  dplyr::arrange(dplyr::desc(missing_listings))

A10
missing_by_city
```


Answer 10: How many listings are under missing_listings? 456 

README: Which city looses the most listings? Chicago with 267

## B2 
```{r}
# Share of listings owned by hosts with 10+ listings
listing_shares = listings_with_counts |>
  dplyr::group_by(city) |>
  dplyr::summarize(
    listing_share = 100 * mean(listing_count >= 10),
    .groups = "drop"
  )

# Revenue earned by each city's top 10% of listings
revenue_shares = revenue_concentration |>
  dplyr::select(city, percentage)


B2 = listing_shares |>
  dplyr::left_join(revenue_shares, by = "city") |>
  dplyr::rename(
    revenue_share = percentage
  )

B2
```

Answer B2: 

Chicago 31.89 listing share 40.73 revenue share 

Columbus 37.14 listing share 36.08 revenue share 

Twin Cities 17.15 listing share 40.26 revenue share 
